---
title: "Appendix C - Replication of Study 1 with Experienced Decision-Makers"
format:
  html:
    code-fold: true
    code-summary: "Show Code"
  pdf:
    toc: false
    number-sections: false

execute:
  warning: false
  message: false
  error: false
  fig-width: 10
  fig-height: 5.5
  fig-dpi: 400
knitr:
  opts_chunk:
    collapse: true
---

We conducted a conceptual replication of Study 1 as part of a classroom exercise with senior executives enrolled in "data-driven decision-making" programs at major European business schools in February, March, and September 2022.

Participants played the same investment simulation as in Study 1, with one modification: the design included only the Increasing and Decreasing conditions (the Flat condition was dropped). After playing 20 rounds, participants completed the same post-game survey measuring their subjective sense of learning, confidence in their attribute judgments, and the extremity of their predictions.

## Preamble: Data Loading and Wrangling

```{r}
library(tidyverse)
library(Hmisc)
library(effsize)
library(glue)
library(gt)
library(here)

i_am("Appendices/AppendixC.qmd")
source(here("custom_theme.R"))

survey_data <- read_csv(
  here("Studies/Appendix_Exec", "Data", "survey_clean.csv")
)

items <- c(
  "SubjInfluence",
  "EdgeOver",
  "BecameConfident",
  "CouldPredict",
  "AttribDiff",
  "NotEnoughRound",
  "N_Correct_Responses",
  "Confidence",
  "Extremity_Bets"
)

labels <- c(
  "Pred. Influence on ROI",
  "Pred. Edge over New Player",
  "Confident in Ability to Predict ROI",
  "Could Predict ROI by End Game",
  "Some Attrib. Were More Predictive",
  "Not Enough Rounds to Learn",
  "# Correct Attributes Comparisons",
  "Confidence in Attributes Comps.",
  "Extremity of Bets"
)
```

## Sample

```{r}
n_total <- nrow(survey_data)
n_per <- survey_data %>% count(Condition)
```

The final sample consisted of `r n_total` executives (`r n_per$n[n_per$Condition == "Increasing"]` in the Increasing condition, `r n_per$n[n_per$Condition == "Decreasing"]` in the Decreasing condition).

## Results

```{r}
# Compute t-tests and effect sizes for all DVs
results <- map_dfr(seq_along(items), function(i) {
  s <- items[i]
  formula <- as.formula(paste(s, "~ Condition"))
  tt <- t.test(formula, data = survey_data)
  cd <- cohen.d(formula, data = survey_data)

  # t.test alphabetical: Decreasing - Increasing.
  # Negate for Increasing - Decreasing.
  tibble(
    DV = labels[i],
    t = -tt$statistic,
    df = tt$parameter,
    p = tt$p.value,
    d = -cd$estimate,
    d_ci_lower = -cd$conf.int[2],
    d_ci_upper = -cd$conf.int[1]
  )
})
```

### Survey Measures

```{r}
#| fig-height: 5.5

# Compute t-stats for annotation
df_results <- results %>%
  mutate(
    formatted_p = ifelse(p < .001, "p < .001", glue("p = {round(p, 3)}")),
    label = glue(
      "t({round(df, 0)}) = {round(t, 3)}",
      "\n{formatted_p}\nd = {round(d, 2)}"
    ),
    item = factor(labels, levels = labels)
  )

# Pivot to long form
survey_data_long <- survey_data %>%
  pivot_longer(cols = all_of(items), names_to = "item") %>%
  dplyr::select(ResponseId, Condition, item, value) %>%
  mutate(item = factor(item, levels = items, labels = labels))

# Compute y-position for annotations
df_results <- df_results %>%
  left_join(
    survey_data_long %>%
      group_by(item) %>%
      summarise(y_pos = mean(value, na.rm = TRUE), .groups = "drop"),
    by = "item"
  )

ggplot(survey_data_long, aes(x = Condition, y = value, color = Condition)) +
  facet_wrap(~item, scales = "free_y") +
  stat_summary(
    fun = mean, geom = "point",
    position = position_dodge(width = 0.5), size = 4
  ) +
  stat_summary(
    fun.data = mean_cl_boot, geom = "errorbar", width = 0,
    position = position_dodge(width = 0.5), show.legend = FALSE,
    linewidth = 1.2
  ) +
  theme_matplotlib() +
  scale_color_manual(values = c("#b63441", "#3f69c9")) +
  labs(
    x = element_blank(),
    color = element_blank(),
    y = "Survey Response"
  ) +
  guides(color = "none") +
  geom_text(
    data = df_results,
    mapping = aes(x = 1.5, y = y_pos, label = label),
    inherit.aes = FALSE,
    color = "black",
    size = 3
  )
```

### Statistical Results

```{r}
results %>%
  mutate(
    d_ci = glue("[{round(d_ci_lower, 2)}, {round(d_ci_upper, 2)}]")
  ) %>%
  dplyr::select(DV, t, df, p, d, d_ci) %>%
  gt() %>%
  cols_label(
    DV = "Dependent Variable",
    t = md("*t*"),
    df = md("*df*"),
    p = md("*p*"),
    d = md("*d*"),
    d_ci = "95% CI"
  ) %>%
  fmt_number(columns = c(t, df), decimals = 1) %>%
  fmt_number(columns = d, decimals = 2) %>%
  fmt(
    columns = p,
    fns = function(x) ifelse(x < .001, "< .001", sprintf("%.3f", x))
  ) %>%
  tab_header(
    title = "Independent-Samples t-Tests: Increasing vs. Decreasing Condition"
  )
```

### Summary

Consistent with the results of Study 1, executives exposed to an improving sequence of outcomes reported a greater subjective understanding of cue-outcome relationships and greater confidence in their ability to generate positive outcomes in the future.
Critically, the number of correct attribute comparisons---the only objective measure of learning---did not differ between conditions (*d* = 0.01, *p* = .974), confirming that the manipulation affected subjective beliefs about learning without improving actual knowledge of the cue-outcome relationships.
