---
title: "Appendix H - Analysis of Testing Strategies in Study 4"
format:
  html:
    code-fold: true
    code-summary: "Show Code"
  pdf:
    toc: false
    number-sections: false

execute:
  warning: false
  message: false
  error: false
  fig-width: 10
  fig-height: 4
  fig-dpi: 400
knitr:
  opts_chunk:
    collapse: true
---

## Preamble: Data Loading and Wrangling

```{r}
library(tidyverse)
library(tidymodels)
library(glue)
library(gt)
library(mlogit)
library(here)

i_am("Appendices/AppendixH.qmd")
source(here("custom_theme.R"))

cols_subj_learn_interim <- c(
    "could_learn_interim_1",
    "could_learn_interim_2",
    "could_learn_interim_3"
)

cols_illusory_beliefs_interim <- c(
    "belief_valuation",
    "belief_market_size",
    "belief_sector_of_activity",
    "belief_competitors"
)

survey_data <- read_csv(here("Studies/Study4", "Data", "survey_clean.csv")) %>%
    mutate(Slope = 2 - Slope) %>%
    rowwise() %>%
    mutate(
        SubjectiveLearning_Interim = mean(c_across(cols_subj_learn_interim)),
        IllusoryBeliefs_Interim = mean(c_across(cols_illusory_beliefs_interim)),
        condition = factor(
            case_when(
                condid == 0 ~ "Flat",
                condid == 1 ~ "Increasing"
            ),
            levels = c("Flat", "Increasing")
        ),
        message_type = factor(
            message_type,
            levels = c("control", "positive_test", "negative_test"),
            labels = c("Control", "Positive\nTest", "Negative\nTest")
        )
    ) %>%
    dplyr::filter(time_to_completion > 110)
```

## Analysis of Testing Strategies

Participants were asked to report the extent to which they used a positive testing strategy (seeking confirming evidence) and a negative testing strategy (seeking disconfirming evidence) in the first half (Rounds 1--10) and second half (Rounds 11--20) of the game.

```{r}
#| fig-width: 10
#| fig-height: 6
testing_strategy <- survey_data %>%
    dplyr::select(
        turkid,
        condid,
        message_type,
        Positive_Test_First,
        Positive_Test_Second,
        Negative_Test_First,
        Negative_Test_Second
    ) %>%
    pivot_longer(
        cols = c(
            Positive_Test_First,
            Positive_Test_Second,
            Negative_Test_First,
            Negative_Test_Second
        )
    ) %>%
    mutate(
        Strategy = str_split(name, "_") %>% map_chr(~ .x[[1]]),
        Timing = str_split(name, "_") %>% map_chr(~ .x[[3]])
    )

label_map_time <- c("First" = "Rounds 1-10", "Second" = "Rounds 11-20")
label_strategy <- c(
    "Positive" = "... a Positive Test Strategy",
    "Negative" = "... a Negative Test Strategy"
)

testing_strategy %>%
    group_by(message_type, Timing, Strategy) %>%
    count(value) %>%
    mutate(pct = n / sum(n)) %>%
    ggplot(aes(x = value, y = pct, fill = message_type)) +
    geom_col(position = position_dodge2(), width = .6) +
    facet_grid(
        Strategy ~ Timing,
        switch = "y",
        labeller = labeller(Timing = label_map_time, Strategy = label_strategy)
    ) +
    scale_fill_manual(values = c("darkgrey", "green4", "red4")) +
    scale_x_continuous(
        breaks = c(1, 2, 3, 4, 5),
        labels = c("Never", "< 50%", "\u2248 50%", "> 50%", "Always")
    ) +
    labs(
        x = element_blank(),
        y = "% of Rounds Reported Using...",
        color = element_blank()
    ) +
    scale_y_continuous(
        limits = c(0, .60),
        breaks = seq(0, .60, by = .10),
        labels = scales::label_percent()
    ) +
    theme_matplotlib() +
    theme(
        strip.placement = "outside",
        strip.text.y.left = element_text(angle = 90, vjust = 0.5, size = 12)
    )
```

The left panels (Rounds 1--10) show that participants rarely used a Negative Test strategy (top panel) and instead favored a Positive Test strategy (bottom panel).

The right panels (Rounds 11--20) confirm the effectiveness of our testing prompt: Participants in the "Negative Test" condition substantially increased their use of a Negative Test strategy (top right panel) and decreased their use of a Positive Test strategy (bottom right panel). In contrast, participants in the "Positive Test" condition further increased their use of a Positive Test strategy while maintaining a low use of a Negative Test strategy.

## Further Evidence of Change in Testing Strategies

A multinomial logit model (estimated on the choices made in Rounds 15--20, after the testing prompt was presented) provides further evidence that the prompt changed participants' testing strategies.

```{r}
# Load and prepare game choices data for the multinomial logit model
choices_data <- read_csv(
    here(
        "Studies/Study4", "Data",
        "game_choices_clean_with_attributes.csv"
    )
) %>%
    arrange(condition) %>%
    rename_with(
        ~ recode(
            .,
            "valuation" = "Valuation",
            "customers" = "Customers",
            "competitors" = "Competitors",
            "round" = "Round",
            "project" = "Project",
            "condition" = "Condition",
            "project_chosen" = "Project_Chosen"
        )
    ) %>%
    mutate(
        Valuation = as.numeric(scale(Valuation)),
        Customers = as.numeric(scale(Customers)),
        Competitors = as.numeric(scale(Competitors)),
        `Biotech` = as.numeric(activity == "Biotechnology"),
        `Electronics` = as.numeric(activity == "Electronics"),
        `Robotics` = as.numeric(activity == "Robotics"),
        Flat = as.numeric(Condition == "Flat"),
        Inc = as.numeric(Condition == "Increasing"),
        Pos = as.numeric(message_type == "positive_test"),
        Neg = as.numeric(message_type == "negative_test"),
        Option_0 = as.numeric(Project == 0),
        Option_1 = as.numeric(Project == 1),
        Option_2 = as.numeric(Project == 2),
        Project_Chosen = as.numeric(Project_Chosen),
        Slope = condid,
        Round = Round - 1
    ) %>%
    dplyr::arrange(turkid, Round, Project)

interaction_columns <- c(
    "Option_1", "Option_2", "Valuation", "Customers", "Competitors",
    "Electronics", "Robotics"
)

for (col in interaction_columns) {
    for (m in c("Pos", "Neg")) {
        choices_data <- choices_data %>%
            mutate(!!paste0(m, "_", col) := !!sym(col) * !!sym(m))
    }
    choices_data <- choices_data %>%
        mutate(
            !!paste0("Slope_", col) := !!sym(col) * Slope,
            !!paste0("Round_", col) := !!sym(col) * Round,
            !!paste0("ThreeWay_", col) := !!sym(col) * Round * Slope
        )
}

choices_data_logit <- choices_data %>%
    mutate(
        choice_occasion = glue("{turkid}_{Round}"),
        turkid = as.integer(factor(turkid))
    ) %>%
    arrange(turkid, Round, Project)

df_mxl <- mlogit.data(
    choices_data_logit %>%
        filter(Round > 14 & Inc == 1) %>%
        as.data.frame() |>
        dplyr::select(
            turkid, choice_occasion, Project, Project_Chosen,
            Customers, Competitors, Valuation, Electronics, Robotics,
            Pos_Customers, Pos_Competitors, Pos_Valuation,
            Pos_Electronics, Pos_Robotics,
            Neg_Customers, Neg_Competitors, Neg_Valuation,
            Neg_Electronics, Neg_Robotics
        ),
    choice = "Project_Chosen",
    shape = "long",
    alt.var = "Project",
    chid.var = "choice_occasion",
    id.var = "turkid"
)

# Estimate the mixed logit model (cached to avoid re-running)
cache_path <- here("Studies/Study4", "Data", "mxl_int_model.rds")

if (file.exists(cache_path)) {
    mxl_int <- readRDS(cache_path)
} else {
    mxl_int <- mlogit(
        Project_Chosen ~
            Customers + Competitors + Valuation +
                Electronics + Robotics +
                Pos_Customers + Pos_Competitors + Pos_Valuation +
                Pos_Electronics + Pos_Robotics +
                Neg_Customers + Neg_Competitors + Neg_Valuation +
                Neg_Electronics + Neg_Robotics |
                0,
        data = df_mxl,
        rpar = c(
            Customers = "n", Competitors = "n", Valuation = "n",
            Electronics = "n", Robotics = "n",
            Pos_Customers = "n", Pos_Competitors = "n", Pos_Valuation = "n",
            Pos_Electronics = "n", Pos_Robotics = "n",
            Neg_Customers = "n", Neg_Competitors = "n", Neg_Valuation = "n",
            Neg_Electronics = "n", Neg_Robotics = "n"
        ),
        correlation = TRUE,
        panel = TRUE,
        R = 1000,
        halton = NA
    )
    saveRDS(mxl_int, cache_path)
}

# Compute marginal effects via contrasts
model_inter_results <- mxl_int %>%
    tidy() %>%
    head(15)

b <- mxl_int$coefficients[1:15]
vcv <- (-solve(mxl_int$hessian)[1:15, 1:15])

k <- 5
contrasts_mat <- rbind(
    cbind(diag(k), 0 * diag(k), 0 * diag(k)), # Control
    cbind(diag(k), diag(k), 0 * diag(k)), # Pos Test
    cbind(diag(k), 0 * diag(k), diag(k)) # Neg Test
)

conts <- as.numeric(contrasts_mat %*% b)
errs <- sqrt(diag(contrasts_mat %*% vcv %*% t(contrasts_mat)))

levels <- c(
    "Customers", "Competitors", "Valuation",
    "Electronics vs. Biotech", "Robotics vs. Biotech"
)
names <- rep(levels, times = 3)

pvals_pos <- ifelse(model_inter_results$p.value < .001, "p < .001",
    glue("p = {sprintf('%.3f', model_inter_results$p.value)}")
)[6:10]
pvals_neg <- ifelse(model_inter_results$p.value < .001, "p < .001",
    glue("p = {sprintf('%.3f', model_inter_results$p.value)}")
)[11:15]
labels <- glue("{levels}\n(Inter_Pos: {pvals_pos})\n(Inter_Neg: {pvals_neg})")

df_contrasts <- data.frame(
    estimate = conts,
    std.error = errs,
    term = names,
    message_type = factor(
        rep(c("Control", "Positive Test", "Negative Test"), each = k),
        levels = c("Control", "Positive Test", "Negative Test")
    ),
    term_names = factor(names, levels = levels, labels = labels)
)

ggplot(
    df_contrasts,
    aes(
        x = estimate, y = term_names,
        color = message_type, shape = message_type, fill = message_type
    )
) +
    geom_point(size = 3, position = position_dodge(width = -.35)) +
    geom_errorbarh(
        aes(
            xmin = estimate - 1.96 * std.error,
            xmax = estimate + 1.96 * std.error
        ),
        height = 0, linewidth = 1,
        position = position_dodge(width = -.35)
    ) +
    labs(
        title = element_blank(),
        x = "Standardized Marginal Effect\n(Estimated on Rounds 15-20 Choices)",
        y = element_blank(),
        color = element_blank(),
        shape = element_blank(),
        fill = element_blank()
    ) +
    theme_matplotlib() +
    scale_x_continuous(breaks = seq(-36, 26, 4) / 10) +
    geom_vline(xintercept = 0, linetype = "dashed") +
    theme(
        axis.text.y = element_text(size = 10),
        axis.text.x = element_text(size = 11),
        legend.position = "top",
        panel.grid.major.y = element_blank(),
        panel.grid.minor.y = element_blank(),
        legend.background = element_rect(
            fill = "white",
            color = "white",
            linewidth = 0
        )
    ) +
    scale_y_discrete(limits = rev) +
    scale_color_manual(values = c("darkgrey", "green4", "red4")) +
    scale_fill_manual(values = c("darkgrey", "green4", "red4")) +
    scale_shape_manual(values = c(21, 24, 25))
```

For participants in the "Control" and "Positive Test" conditions, the Number of Customers and Market Valuation are significant predictors of a project being chosen, and the Number of Competitors is a negative predictor. For participants in the "Negative Test" condition, the pattern reverses: these participants shift their selections toward attributes they had previously ignored, consistent with the adoption of a negative testing strategy.

## Belief Regarding the Slope

Finally, participants were asked to identify the slope condition they were assigned to.

```{r}
#| fig-height: 3.5
survey_data |>
    group_by(condition) %>%
    count(Slope) %>%
    mutate(pct = n / sum(n)) %>%
    ggplot(aes(x = Slope, y = pct, fill = condition)) +
    geom_col(position = position_dodge2(), width = .5) +
    scale_fill_manual(values = c("#1f1e1e", "#3f69c9")) +
    scale_x_continuous(
        breaks = c(-1, 0, 1),
        labels = c("Slope was Decreasing", "Slope was Flat", "Slope was Increasing")
    ) +
    theme_matplotlib() +
    labs(
        x = element_blank(),
        y = "% of Participants Reporting That...",
        fill = element_blank()
    )
```

Most participants correctly identified their assigned condition: They realized that the "Increasing" condition had an increasing exogenous slope, and that the "Flat" condition had no slope.

## Slope Beliefs by Prompt Type (Increasing Condition)

Among participants in the "Increasing" condition, we further examine whether slope beliefs differed by prompt type.

```{r}
#| fig-height: 3.5
library(Hmisc)
survey_data %>%
    dplyr::filter(condition == "Increasing") %>%
    mutate(said_increasing = as.numeric(Slope == 1)) %>%
    ggplot(aes(x = message_type, y = said_increasing, color = message_type)) +
    stat_summary(fun.data = mean_cl_boot, geom = "pointrange", size = .8) +
    scale_color_manual(values = c("darkgrey", "green4", "red4")) +
    scale_y_continuous(
        labels = scales::label_percent(),
        limits = c(0, 1)
    ) +
    theme_matplotlib() +
    labs(
        x = element_blank(),
        y = "% Reporting the Slope Was Increasing",
        color = element_blank()
    ) +
    theme(legend.position = "none")
```
