---
title: "Results - Social Media"
format: html
editor: visual
execute: 
  warning: false
  error: false
  
editor_options: 
  chunk_output_type: inline
---

# Data Processing

## Library and Functions

```{r}
library(dplyr, warn.conflicts = FALSE)
options(dplyr.summarise.inform = FALSE)
library(tidyverse)
library(lme4)
library(lmerTest)
library(tidymodels)
library(glue)
library(lfe)
library(ltm)
library(here)

i_am("Studies/Study3b/Code/Analysis.qmd")

mean_and_ci <- function(grouped_data, var) {
  grouped_data %>%
    summarise(
      mean = mean({{ var }}, na.rm = TRUE),
      sd = sd({{ var }}, na.rm = TRUE),
      n = n()
    ) %>%
    mutate(
      se = sd / sqrt(n),
      llci = mean - qt(1 - (0.05 / 2), n - 1) * se,
      ulci = mean + qt(1 - (0.05 / 2), n - 1) * se
    )
}

generate_title <- function(model, alpha=NULL) {
  coeffs <- model %>% tidy()
  summ <- model %>% glance()
  df <- summ %>%
    slice(1) %>%
    pull(df.residual)
  t <- coeffs %>%
    slice(2) %>%
    pull(statistic)
  pval <- coeffs %>%
    slice(2) %>%
    pull(p.value)
  glue(
    "t({df}) = {round(t, 3)}, {ifelse(pval < .001, 'p < .001', glue('p = {round(pval, 3)}'))}"
  )
}

expand_combinations <- function(..., sep="_"){ 
  grid <- expand.grid(...) 
  grid %>% tidyr::unite("Result", everything(), sep=sep) %>% pull(Result) 
  }


calculate_gini <- function(x) {
  x <- sort(x)
  n <- length(x)
  G <- 2 * sum((1:n) * x) / (n * sum(x)) - (n + 1) / n
  return(G)
}

calculate_entropy <- function(x) {
  return(-sum(ifelse(x > 0, x * log2(x), 0)))
}

calculate_beliefs_disp <- function(split, variable) {
  analysis(split) %>%
    group_by(condition, {{variable}}, .drop = FALSE) %>%
    summarise(n = n()) %>%
    mutate(prop = n / sum(n)) %>%
    ungroup() %>%
    group_by(condition) %>%
    summarise(
      Gini = calculate_gini(n),
      HHI = sum((prop * 100)^2),
      Entropy = calculate_entropy(prop),
    )
}
```

## Reading and Cleaning Data

```{r setup, warning=false}
game_data <- read_csv(here("Studies/Study3b", "Data", "game_data_clean.csv")) %>% drop_na(turkid)

game_data_diff <- game_data %>%
  mutate(gameduration = enddate - startdate) %>%
  filter(gameduration > 50) %>% 
  group_by(turkid) %>%
  mutate(across(
    c(Hook, Length, Tone, Content, CallToAction),
    ~ ifelse(.x != lag(.x), 1, 0),
    .names = "Changed_{col}"
  )) %>%
    mutate(across(
    c(Hook, Length, Tone, Content, CallToAction),
    ~ ifelse(.x != .x[1], 1, 0),
    .names = "From_First_Changed_{col}"
  )) %>%
  mutate(timetochoose = as.numeric(choicestimes - lag(choicestimes))) %>%
  ungroup() %>%
  mutate(n_changes = rowSums(dplyr::select(., starts_with("Changed_"))),
         n_changes_from_first= rowSums(dplyr::select(., starts_with("From_First_Changed_")))) %>%
  drop_na(Changed_Hook, turkid)

game_data_short <-
  game_data_diff %>%
  group_by(turkid, week) %>%
  summarise(
    gameduration = mean(gameduration),
    n_changes =
      mean(n_changes),
    n_zero_changes =
      mean(n_changes == 0)
  ) %>%
  group_by(turkid) %>%
  summarise(
    gameduration = mean(gameduration),
    n_changes =
      mean(n_changes),
    n_zero_changes =
      mean(n_zero_changes)
  )


data_wide <- game_data %>%
  dplyr::select(turkid, week, Hook, Length, Tone, Content, CallToAction) %>%
  group_by(turkid, week) %>%
  mutate(choice_vector = list(c(Hook, Length, Tone, Content, CallToAction))) %>%
  dplyr::select(turkid, week, choice_vector) %>%
  pivot_wider(names_from = week, values_from = choice_vector) %>%
  ungroup()

hamming_distance <- function(vec1, vec2) {
  sum(vec1 != vec2)
}

calculate_distances <- function(row) {
  # Generate all combinations of rounds (assuming 3 rounds)
  combinations <- combn(x = row, m = 2, simplify = FALSE)
  # Calculate the Hamming distance for each pair
  sapply(combinations, function(pair) hamming_distance(pair[[1]], pair[[2]]))
}

hamming_dist <- data_wide %>% dplyr::select(turkid) %>% mutate(hamming_dist=rowMeans(t(apply(data_wide[, -1], 1, calculate_distances))))

survey_data <-
  read_csv(here("Studies/Study3b", "Data", "survey_clean.csv")) %>%
  left_join(game_data_short) %>%
  drop_na(turkid) %>%
  ungroup() %>%
  left_join(hamming_dist) %>%
  left_join(game_data %>% group_by(turkid) %>% summarise(n_distinct = n_distinct(Hook, Length, Tone, Content, CallToAction)) %>% dplyr::select(turkid, n_distinct)) %>%
  left_join(game_data %>% group_by(turkid) %>% mutate(across(c(Hook, Length, Tone, Content, CallToAction), ~ as.numeric(.x == lag(.x, 7)))) %>% filter(row_number()==8) %>% rowwise() %>% mutate(changes_from_orig = sum(CallToAction, Content, Hook, Length, Tone)) %>% dplyr::select(turkid, changes_from_orig))

survey_data_clean <-
  survey_data %>%
  mutate(
    DV_4 = -DV_4_R,
    condition = factor(
      condid,
      levels = c(0, 1),
      labels = c("Flat", "Increasing")
    )
  ) %>%
  mutate(
    AttributesPredict = rowMeans(dplyr::select(., c(DV_1, DV_2, DV_3, DV_4))) + 3,
    SubjectiveKnowledge = rowMeans(dplyr::select(., c(CouldLearn_1, CouldLearn_2, CouldLearn_3))) + 3,
    included = gameduration > 50
  ) %>%
  filter(included)

game_data_long <- survey_data_clean %>%
  dplyr::select(turkid, `1_Hook`:`2_CTA`) %>%
  rename(
    Best_Tone = `1_Tone`,
    Best_CallToAction = `1_CTA`,
    Best_Content = `1_Content`,
    Best_Hook = `1_Hook`,
    Best_Length = `1_Length`,
    Worst_Tone = `2_Tone`,
    Worst_CallToAction = `2_CTA`,
    Worst_Content = `2_Content`,
    Worst_Hook = `2_Hook`,
    Worst_Length = `2_Length`
  ) %>%
  right_join(game_data, by = join_by(turkid)) %>%
  mutate(
    Is_Best_Tone = (Best_Tone == Tone) * 1,
    Is_Best_Content = (Best_Content == Content) * 1,
    Is_Best_CallToAction = (Best_CallToAction == CallToAction) * 1,
    Is_Best_Hook = (Best_Hook == Hook) * 1,
    Is_Best_Length = (Best_Length == Length) * 1,
    Is_Worst_Tone = (Worst_Tone == Tone) * 1,
    Is_Worst_Content = (Worst_Content == Content) * 1,
    Is_Worst_CallToAction = (Worst_CallToAction == CallToAction) * 1,
    Is_Worst_Hook = (Worst_Hook == Hook) * 1,
    Is_Worst_Length = (Worst_Length == Length) * 1,
  ) %>%
  rowwise() %>%
  mutate(Is_Best_Avg = mean(c(
    Is_Best_Tone, Is_Best_Content, Is_Best_CallToAction,
    Is_Best_Hook, Is_Best_Length)),
    Is_Worst_Avg = mean(c(
    Is_Worst_Tone, Is_Worst_Content, Is_Worst_CallToAction,
    Is_Worst_Hook, Is_Worst_Length
  ))) %>% drop_na(Best_CallToAction)


survey_data_choices <- survey_data_clean %>%
  unite(
    Best_Posts,
    c(`1_Hook`, `1_Length`, `1_Tone`, `1_Content`, `1_CTA`),
    remove = FALSE
  ) %>%
  unite(
    Worst_Posts,
    c(`2_Hook`, `2_Length`, `2_Tone`, `2_Content`, `2_CTA`),
    remove = FALSE
  ) %>%
  unite(
    Best_Posts_HookLength,
    c(`1_Hook`, `1_Length`),
    remove = FALSE
  ) %>%
  unite(
    Best_Posts_ToneContentCTA,
    c(`1_Tone`, `1_Content`, `1_CTA`),
    remove = FALSE
  ) %>%
  unite(
    Worst_Posts_HookLength,
    c(`2_Hook`, `2_Length`),
    remove = FALSE
  ) %>%
  unite(
    Worst_Posts_ToneContentCTA,
    c(`2_Tone`, `2_Content`, `2_CTA`),
    remove = FALSE
  ) %>%
  mutate(
    Best_Posts = factor(Best_Posts,
      levels = expand_combinations(c(0, 1, 2), c(0, 1, 2), c(0, 1), c(0, 1, 2), c(0, 1))
    ),
    Worst_Posts = factor(Worst_Posts,
      levels = expand_combinations(c(0, 1, 2), c(0, 1, 2), c(0, 1), c(0, 1, 2), c(0, 1))
    ),
    Best_Posts_HookLength = factor(Best_Posts_HookLength,
      levels = expand_combinations(c(0, 1, 2), c(0, 1, 2)),
      labels = expand_combinations(c("Question", "Cliffhanger", "Anecdote"),
        c("< 400 words", "400-1400 words", "1400-2400 words"),
        sep = " - "
      )
    ),
    Best_Posts_ToneContentCTA = factor(Best_Posts_ToneContentCTA,
      levels = expand_combinations(c(0, 1), c(0, 1, 2), c(0, 1)),
      labels = expand_combinations(c("First P.", "Third P."), c("Text", "Text+Pic", "Text+Poll"), c("CTA", "No CTA"), sep = " - ")
    ),
    Worst_Posts_HookLength = factor(Worst_Posts_HookLength,
      levels = expand_combinations(c(0, 1, 2), c(0, 1, 2)),
      labels = expand_combinations(c("Question", "Cliffhanger", "Anecdote"),
        c("< 400 words", "400-1400 words", "1400-2400 words"),
        sep = " - "
      )
    ),
    Worst_Posts_ToneContentCTA = factor(Worst_Posts_ToneContentCTA,
      levels = expand_combinations(c(0, 1), c(0, 1, 2), c(0, 1)),
      labels = expand_combinations(c("First P.", "Third P."),
        c("Text", "Text+Pic", "Text+Poll"),
        c("CTA", "No CTA"),
        sep = " - "
      )
    )
  )

survey_data_clean %>% write_csv(here("Studies/Study3b", "Data", "survey_data_clean.csv"))
game_data_long %>% write_csv(here("Studies/Study3b", "Data", "game_data_long.csv"))
game_data_diff %>% write_csv(here("Studies/Study3b", "Data", "game_data_diff.csv"))
```

# Pre-Registered Analysis

## Subjective Knowledge

```{r}
alpha_su <- cronbach.alpha(survey_data_clean %>% dplyr::select(CouldLearn_1:CouldLearn_3))$alpha
model <-
  lm(SubjectiveKnowledge ~ condition, data = survey_data_clean)

survey_data_clean %>%
  group_by(condition) %>%
  mean_and_ci(SubjectiveKnowledge) %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1) +
  geom_point() +
  labs(
    x = element_blank(),
    y = glue("Subjective Knowledge (1-5; α = {round(alpha_su, 2)})"),
    title = generate_title(model)
  ) + theme_light() + theme(panel.grid.major.x=element_blank())
```

## Belief that Cues Influenced Outcomes

```{r}
model <-
  lm(AttributesPredict ~ condition, data = survey_data_clean)
alpha_ap <- cronbach.alpha(survey_data_clean %>% drop_na(c(DV_1, DV_2, DV_3, DV_4)) %>% dplyr::select(DV_1, DV_2, DV_3, DV_4))$alpha
survey_data_clean %>%
  group_by(condition) %>%
  mean_and_ci(AttributesPredict) %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1) +
  geom_point() +
  labs(
    x = element_blank(),
    y = glue("Attributes Influence Outcomes (1-5; α = {round(alpha_ap, 2)})"),
    title = generate_title(model)
  ) + theme_light() + theme(panel.grid.major.x=element_blank())
```

## Subjective Likelihood of Superiority

Subjective probability that the "best" post would outperform the "worst" post in likes:

```{r}
model <-
  lm(EdgeProbability ~ condition, data = survey_data_clean)

survey_data_clean %>%
  group_by(condition) %>%
  mean_and_ci(EdgeProbability) %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1) +
  geom_point() +
  labs(
    x = element_blank(),
    y = "Probability of 'Best'\nOutperforming 'Worst' (50-100)",
    title = generate_title(model)
  ) + theme_light() + theme(panel.grid.major.x=element_blank())
```

```{r}
model <-
  lm(changes_from_orig ~ condition, data = survey_data_clean)

survey_data_clean %>%
  group_by(condition) %>%
  mean_and_ci(changes_from_orig) %>%
  ggplot(aes(x = condition, y = mean)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1) +
  geom_point() +
  labs(
    x = element_blank(),
    y = "Probability of 'Best'\nOutperforming 'Worst' (50-100)",
    title = generate_title(model)
  ) + theme_light() + theme(panel.grid.major.x=element_blank())
```

# Exploratory Analysis

## Number of Attributes Changed from First Choice

```{r}
game_data_diff %>%
  group_by(condition, week) %>%
  mean_and_ci(n_changes_from_first) %>%
  ungroup() %>% 
  ggplot(aes(x = week, y = mean, color = condition)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1, position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  labs(y = "Number of Attributes Changed\nfrom First Decision", x = element_blank()) +
  scale_x_continuous(breaks = seq(2, 8, 1), labels = glue("Round {seq(2, 8)}"), minor_breaks = c())  + geom_smooth(data=game_data_diff, aes(x = week, y = n_changes_from_first, color = condition), method="lm", alpha=.3, formula=y~x)+ theme_light() +
  theme(legend.title = element_blank())
```

## Number of Attribute Changes During the Game

Participants could change, each round, between 0 and 5 attributes. How many did they change, and this value differ over time and across conditions?

```{r}
game_data_diff %>%
  group_by(condition, week) %>%
  mean_and_ci(n_changes) %>%
  ungroup() %>% 
  ggplot(aes(x = week, y = mean, color = condition)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1, position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  labs(y = "Number of Attributes Changed\nfrom Previous Round", x = element_blank()) +
  scale_x_continuous(breaks = seq(2, 8, 1), labels = glue("Round {seq(1, 7)}\nto {seq(2, 8)}"), minor_breaks = c())  + geom_smooth(data=game_data_diff, aes(x = week, y = n_changes, color = condition), method="lm", alpha=.3, formula=y~x)+ theme_light() +
  theme(legend.title = element_blank())
```

We find evidence that, as the game goes on, participants in the "Increasing" condition change fewer attributes, suggesting that they are converging on a set of "predictive" attributes.

A linear model with cluster-robust standard errors at the participant level, confirms the significance of this pattern:

```{r}
summary(felm(n_changes~week*condition | 0 |0 |turkid, data=game_data_diff))
```

Another explanation for this pattern would be that participants in the "Increasing" condition start "exploiting": They deliberate less, and simply choose what they chose before.

If this is the case however, we should see that they take less time making their decisions:

```{r}
game_data_diff %>%
  group_by(condition, week) %>%
  mean_and_ci(timetochoose) %>%
  ungroup() %>%
  ggplot(aes(x = week, y = mean, color = condition)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1, position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  labs(y = "Time Between Choices", x = element_blank()) +
  scale_x_continuous(breaks = seq(2, 8, 1), labels = glue("Round {seq(1, 7)}\nto {seq(2, 8)}"), minor_breaks = c()) +
  geom_smooth(data = game_data_diff, aes(x = week, y = timetochoose, color = condition), method = "lm", alpha = .3, formula = y ~ x) +
  theme_light() +
  theme(legend.title = element_blank())
```

We do not see that. While participants become faster to choose after Round 2, there is no evidence that participants in the "Increasing" condition choose faster than participants in the "Flat" condition.

```{r}
summary(felm(timetochoose~week*condition | 0 |0 |turkid, data=game_data_diff))
```

## Correspondence Between Choices and 'Best' ('Worst') Practices

```{r}
game_data_long %>%
  group_by(condition, week) %>%
  mean_and_ci(Is_Best_Avg) %>%
  ungroup() %>%
  ggplot(aes(x = week, y = mean, color = condition)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1, position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  labs(y = "Percentage of Attributes\nIn Agreement with 'Best Practices'", x = element_blank()) +
  scale_x_continuous(breaks = seq(1, 8, 1), labels = glue("Round {seq(1, 8)}"), minor_breaks = c()) +
  geom_smooth(data = game_data_long, aes(x = week, y = Is_Best_Avg, color = condition), method = "lm", alpha = .3, formula = y ~ x) +
  theme_light() +
  theme(legend.title = element_blank())

```

```{r}
game_data_long %>%
  group_by(condition, week) %>%
  mean_and_ci(Is_Worst_Avg) %>%
  ungroup() %>%
  ggplot(aes(x = week, y = mean, color = condition)) +
  geom_errorbar(aes(ymin = llci, ymax = ulci), width = .1, position = position_dodge(width = .3)) +
  geom_point(position = position_dodge(width = .3)) +
  labs(y = "Percentage of Attributes\nIn Agreement with 'Worst Practices'", x = element_blank()) +
  scale_x_continuous(breaks = seq(1, 8, 1), labels = glue("Round {seq(1, 8)}"), minor_breaks = c()) +
  geom_smooth(data = game_data_long, aes(x = week, y = Is_Worst_Avg, color = condition), method = "lm", alpha = .3, formula = y ~ x) +
  theme_light() +
  theme(legend.title = element_blank())

```

## Analysis of Best/Worst Features

### Dispersion of Beliefs for Best Features

```{r}
beliefs_dist_best <- survey_data_choices %>%
  group_by(condition, Best_Posts, .drop = FALSE) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  group_by(condition) %>%
  mutate(z = factor(fct_reorder(Best_Posts, desc(n)), labels = seq(1:108)))
beliefs_dist_best %>% ggplot(aes(x = z, y = prop, fill = condition)) +
  geom_bar(stat = "identity", width = 1, position = position_dodge()) +
  geom_hline(yintercept = 1 / 108) +
  labs(y = "% Identifying as 'Best'", x = "Unique Feature Combinations (Sorted by Popularity)", title = "Beliefs About Best Features") +
  annotate("text", x = 65, y = 1 / 50, label = "Expected Under Random Beliefs") +
  theme(axis.text.x = element_blank())

```

```{r}
beliefs_splits <- bootstraps(survey_data_choices, times = 1000)
boot_beliefs_best <- beliefs_splits %>%
  mutate(Beliefs = map(splits, ~calculate_beliefs_disp(.x, variable=Best_Posts))) %>%
  unnest(Beliefs)

diff_beliefs_best <- boot_beliefs_best %>%
  group_by(id) %>%
  mutate(across(c(Gini, HHI, Entropy), function(x){x - lag(x)})) %>% dplyr::select(id:Entropy) %>% drop_na(Gini)

```

```{r}
boot_ci_best <- diff_beliefs_best %>%
  pull(Entropy) %>%
  quantile(c(.025, 0.975))
ggplot(boot_beliefs_best, aes(x = Entropy, fill = condition)) +
  geom_histogram(bins = 30, position = "identity", alpha = .6) +
  labs(
    title = glue("Boot 95% CI of Difference: [{round(boot_ci_best[1], 3)}, {round(boot_ci_best[2], 3)}]"),
    y = element_blank(), x = "Shannon Entropy"
  )
```

```{r}
boot_ci_best <- diff_beliefs_best %>%
  pull(Gini) %>%
  quantile(c(.025, 0.975))
ggplot(boot_beliefs_best, aes(x = Gini, fill = condition)) +
  geom_histogram(bins = 30, position = "identity", alpha = .6) +
  labs(
    title = glue("Boot 95% CI of Difference: [{round(boot_ci_best[1], 3)}, {round(boot_ci_best[2], 3)}]"),
    y = element_blank(), x = "Gini Coefficient"
  )
```

```{r}
boot_ci_best <- diff_beliefs_best %>% 
  pull(HHI) %>%
  quantile(c(.025, 0.975))
ggplot(boot_beliefs_best, aes(x=HHI, fill=condition)) +
  geom_histogram(bins = 30, position="identity", alpha=.6) + labs(title=glue("Boot 95% CI of Difference: [{round(boot_ci_best[1], 3)}, {round(boot_ci_best[2], 3)}]"),
                                                                  y=element_blank(), x="Herfindahl-Hirschman Index")
```

### Dispersion of Beliefs for Worst Features

```{r}
beliefs_dist_worst <- survey_data_choices %>%
  group_by(condition, Worst_Posts, .drop = FALSE) %>%
  summarise(n = n()) %>%
  mutate(prop = n / sum(n)) %>%
  ungroup() %>%
  group_by(condition) %>%
  mutate(z = factor(fct_reorder(Worst_Posts, desc(n)), labels = seq(1:108)))
beliefs_dist_worst %>% ggplot(aes(x = z, y = prop, fill = condition)) +
  geom_bar(stat = "identity", width = 1, position = position_dodge()) +
  geom_hline(yintercept = 1 / 108) +
  labs(y = "% Identifying as 'Worst'", x = "Unique Feature Combinations (Sorted by Popularity)", title = "Beliefs About Worst Features") +
  annotate("text", x = 65, y = 1 / 50, label = "Expected Under Random Beliefs") +
  theme(axis.text.x = element_blank())
```

```{r}
boot_beliefs_worst <- beliefs_splits %>%
  mutate(Beliefs = map(splits, ~calculate_beliefs_disp(.x, variable=Worst_Posts))) %>%
  unnest(Beliefs)

diff_beliefs_worst <- boot_beliefs_worst %>%
  group_by(id) %>%
  mutate(across(c(Gini, HHI, Entropy), function(x){x - lag(x)})) %>% dplyr::select(id:Entropy) %>% drop_na(Gini)

```

```{r}
boot_ci_worst <- diff_beliefs_worst %>%
  pull(Entropy) %>%
  quantile(c(.025, 0.975))
ggplot(boot_beliefs_worst, aes(x = Entropy, fill = condition)) +
  geom_histogram(bins = 30, position = "identity", alpha = .6) +
  labs(
    title = glue("Boot 95% CI of Difference: [{round(boot_ci_best[1], 3)}, {round(boot_ci_best[2], 3)}]"),
    y = element_blank(), x = "Shannon Entropy"
  )
```

```{r}
boot_ci_worst <- diff_beliefs_worst %>%
  pull(Gini) %>%
  quantile(c(.025, 0.975))
ggplot(boot_beliefs_worst, aes(x = Gini, fill = condition)) +
  geom_histogram(bins = 30, position = "identity", alpha = .6) +
  labs(
    title = glue("Boot 95% CI of Difference: [{round(boot_ci_best[1], 3)}, {round(boot_ci_best[2], 3)}]"),
    y = element_blank(), x = "Gini Coefficient"
  )
```

```{r}
boot_ci_worst <- diff_beliefs_worst %>% 
  pull(HHI) %>%
  quantile(c(.025, 0.975))
ggplot(boot_beliefs_worst, aes(x=HHI, fill=condition)) +
  geom_histogram(bins = 30, position="identity", alpha=.6) + labs(title=glue("Boot 95% CI of Difference: [{round(boot_ci_best[1], 3)}, {round(boot_ci_best[2], 3)}]"),
                                                                  y=element_blank(), x="Herfindahl-Hirschman Index")
```

### Descriptive Table - Beliefs

```{r}
#| fig-height: 6
table_best <- as.data.frame(table(survey_data_choices$Best_Posts_HookLength, survey_data_choices$Best_Posts_ToneContentCTA))
table_best$Judgment <- "Best"




table_worst <- as.data.frame(table(survey_data_choices$Worst_Posts_HookLength, survey_data_choices$Worst_Posts_ToneContentCTA))
table_worst$Judgment <- "Worst"

tables <- rbind(table_best, table_worst)

ggplot(tables, aes(x = Var2, y = Var1, fill = Freq)) +
  geom_tile() +
  geom_text(aes(label = Freq)) +
  labs(
    y = "Hook and Length",
    x = "Tone, Content, and CTA"
  ) +
  guides(fill = "none")+ theme(axis.text.x = element_text(angle = 90, vjust = 0.5, 
                                                          hjust=1)) + facet_grid(Judgment~.)

```

```{r}
# Selecting winner
set.seed(242504) # Date
survey_data_clean %>%
  filter(EdgeProbability == 50) %>%
  sample_n(1) %>%
  dplyr::select(turkid, condid)
```